Evaluating Storage Systems for Scientific Data in the Cloud

### 2014-05-10 paper.tex
small comment
lx

\usepackage{comment}
\usepackage{listings}
\usepackage{pgf}
\usepackage{amsmath}
\usepackage{subfigure}
\usepackage{tikz}
\usetikzlibrary{arrows,automata}

@@

\section{Introduction}
%TODO: Improve introduction, we're not talking about exascale
Clouds are poised to become a key platform for data-intensive distributed 
computing~\cite{cloudreq}. Through virtualization, clouds offer full ownership
of a flexible and customizable infrastructure. The Magellan
initiative on cloud usability and data management~\cite{magellan1} examined the
cloud model for scientific applications. One of the challenges identified in
its final report~\cite{magellan2} was developing appropriate application
programming models that enhance the capabilities of the existing MapReduce
model:

@@

>>>>

\usepackage{comment}
\usepackage{listings}
\usepackage{pgf}
\usepackage{amsmath}
\usepackage{subfigure}
\usepackage{tikz}
\usepackage{tikz-qtree}
\usetikzlibrary{arrows,automata}

@@

\section{Introduction}
%TODO: Improve introduction, we're not talking about exascale
%TODO: Add a clear plan for the paper: a hierarchical diagram of things we are addressing in the paper. And things we are not.

Clouds are poised to become a key platform for data-intensive distributed 
computing~\cite{cloudreq}. Through virtualization, clouds offer full ownership
of a flexible and customizable infrastructure. The Magellan
initiative on cloud usability and data management~\cite{magellan1} examined the
cloud model for scientific applications. One of the challenges identified in
its final report~\cite{magellan2} was developing appropriate application
programming models that enhance the capabilities of the existing MapReduce
model:

@@

% ===== 
\tikzset{edge from parent/.style=
{draw, edge from parent path={(\tikzparentnode.south)
-- +(0,-8pt)
-| (\tikzchildnode)}},
blank/.style={draw=none}}
\begin{tikzpicture}
\matrix
{
\node{\Tree 
 [.{the Cloud} 
    [.Compute [.proc-speed  proc-type proc-count ] ] [.Network [.BW Latency] ] [.Storage [.Local EBS Remote-online Remote-offline ]]]};\\
};           
\end{tikzpicture}
% =====
